Introduction to Structural Causal Models

### 2021-05-21 presentation_video.Rmd
xyz

---
title: "A Gentle Introduction to Structural Causal Models"
author: "Daniel Saggau"
date: "5/11/2021"
citation_package: --biblatex
bibliography: [ref.bib]
output: 
  beamer_presentation:
    theme: Madrid

---

@@

@@

- Nodes 
- Edges
- Parents/Ancestors
-

>>>>

---
title: "Introduction to Structural Causal Models"
author: "Daniel Saggau"
date: "5/11/2021"
citation_package: --biblatex
bibliography: [ref.bib]
output: 
  beamer_presentation:
    theme: Madrid
header-includes:
- \definecolor{UBCblue}{rgb}{0.04706, 0.13725, 0.26667}
- \usecolortheme[named=UBCblue]{structure}
---

@@

# Example Intevention

```{r}

```

@@

- Nodes 
- Edges
- Parents/Ancestors/Descendents
- (Missing) Arrows
